Enforced Invariant Confluence

### 2018-04-22 doc/paper/sections/conclusion.tex
First stab at conclusion.

\section{Conclusion}
TODO

>>>>

\section{Conclusion}
This paper revolved around two major contributions.  First, we developed a
deeper understanding of invariant-closure and invariant-confluence by looking
at the two criteria with reachability in mind. We found that invariant-closure
fails to incorporate a notion of reachability, and using this intuition, we
developed conditions under which invariant-closure and invariant-confluence are
equivalent. Second, we proposed a new consistency model and generalization of
invariant-confluence, segmented invariant-confluence, that can be used to
replicate non-invariant-confluent objects with a small amount of coordination
while still preserving their invariants. We also found that segmented
invariant-confluence naturally subsumes existing techniques for maintaining
invariants of replicated objects (e.g.\ locking and escrow transactions).
